\section{Geometric Transport Architecture and Hybrid Feistel Networks}
\label{sec:geometry}

The foundational functional core of the \textsc{Algebirc} engine operates entirely within the `Algebirc.Geometry.GeometricPipeline` and is encoded pre-transport by the `Algebirc.Obfuscation.NonlinearTransform` module. We mandate an extreme hybrid network architecture where code coefficients are not directly mapped to the curve manifold; instead, they must first survive harsh nonlinear diffusion. This dual-layer protection model fuses a Fermat-Inverse based Substitution Box (S-Box) with a quadratic Feistel Network, ultimately encoding the output as parameter groups (Mumford Divisors) for Genus-2 Jacobian transport.

\subsection{Phase 1: Deterministic Fermat-Inverse S-Box Network}
To guarantee the absolute absence of linear patterns from the first clock cycle of execution, every source code atom is extracted into a reduced \textit{Word64} integer across the $GF(p)$ ring. These elements are aggressively injected into the Substitution Box (S-Box). The S-Box is mathematically designed as a singular bijective permutation invoking the Fermat Inversion Algorithm combined with an asymmetric Affine transformation:
\begin{equation}
    S(x) = M \cdot \left( x^{p-2} \bmod p \right) + C \pmod p
\end{equation}
If and only if the input is absolute zero ($x=0$), the \textsc{Algebirc} S-Box forces a mapping to a highly specific prime scalar $37 \cdot (p \div 7) + 19$. A pseudo-deterministic random permutation module—derived via a Fisher-Yates shuffle utilizing a Linear Congruential Generator (LCG)—dynamically generates the random keys surrounding this S-Box constant statically during the initial compilation phase. The Algebraic Normal Form (ANF) complexity of a single S-Box round aggressively spikes to a maximum degree of $p-2$. This mathematically severs any possibility of rendering the box uniformly via trivial linear polynomial regression.

\subsection{Phase 2: Full-Width Add-Rotate-XOR (ARX) Diffusion}
Generating an unconditional avalanche effect specifically mandates that an individual bit derivation must inherently mutate the entire coefficient distribution chain. The ARX function encapsulated within `Algebirc` simulates this entanglement weave through a staggered triple-pass operation (Fwd $\to$ Bwd $\to$ Cross-mix):
\begin{algorithm}[H]
\caption{ARX Coefficient Diffusion over $GF(p)$}
\begin{algorithmic}[1]
\State $X \gets \text{Input Field Coefficients}$
\State $\text{Fwd}[0] \gets X[0]$
\For{$i = 1 \dots N-1$}
    \State $\text{Fwd}[i] \gets (X[i] + S(\text{Fwd}[i-1]) + C_1) \bmod p$
\EndFor
\State $\text{Bwd}[N-1] \gets \text{Fwd}[N-1]$
\For{$j = N-2 \dots 0$}
    \State $\text{Bwd}[j] \gets (\text{Fwd}[j] + S(\text{Bwd}[j+1]) + C_2) \bmod p$
\EndFor
\State $\text{Mixed}[i] \gets S(\text{Bwd}[i] + \text{Bwd}[(i + N/3) \bmod N]) \bmod p$
\State \Return $\text{Mixed}$
\end{algorithmic}
\label{alg:arx}
\end{algorithm}
This inherently non-sequential lexical function actively suppresses standard Differential Cryptanalysis vectors because any generated differential trail is instantaneously crushed on the inverse backward sweep matrix formulation.

\subsection{Phase 3: Jacobian Variety Formation and Mumford Elevation}
After pre-smashing through the cryptographic sponge layers of the Feistel-ARX network, data arrives at the geometric algebraic transformation gate. Every paired scalar coefficient $(c_i, c_{i+1})$ is mathematically elevated (lifted) into a fundamental polynomial coordinate $U$:
\begin{equation}
    u(x) = x^2 + c_i x + c_{i+1}
\end{equation}
Subsequently, the residual curve components are evaluated. For an imaginary hyperelliptic curve $\mathcal{C}: y^2 = f(x)$, the sheer existence of a valid divisor mathematically mandates that the polynomial $v(x)$ fulfills the congruence partition $v^2 \equiv f \pmod u$. Because \textsc{Algebirc} solely manipulates pure $GF(p)$ fields, a Tonelli-Shanks equivalent algorithm tailored for polynomial residues executes to entrap $v(x)$. If the functional resolution of element $v$ falters due to a non-existent factor parameter, the "Parametric CM Action Multiplier" triggers a regeneration loop until the residue calculates positively. This data securely reincarnates as a unique divisor class floating upon the Abelian surface, unrestrictedly navigating the local Jacobians topology.

\subsection{Phase 4: The $(2,2)$ Richelot Isogeny Transport Walk}
The isogeny $\phi: J_\mathcal{C} \to J_{\mathcal{C}'}$ constitutes a critical graph navigation tool. Throughout this trajectory, the mapped coefficient matrices are absorbed into a mathematically dense partial evaluation algorithm where:
\begin{theorem}[Kunzweiler Correspondence Protocol]
Given a Genus-2 hyperelliptic curve, every explicit isogeny transformation targeting an affine divisor $D \mapsto \phi(D)$ is executed by directly substituting the crossed Jacobian parameters without sacrificing a true polynomial parameter correspondence, guaranteeing an exact zero-footprint mapping.
\end{theorem}
As an intensive graph walk computation, the Jacobian spatial momentum hurls forward across a targeted isogeny length parameter ($k \ge 10$) measuring the iteration sequence. This pseudo-chain trajectory massively accelerates the graph reconstruction complexity for reverse-engineers actively attempting backtrack tracing logic, effectively mirroring the Supersingular Isogeny Graph Problem constructed directly atop a 3-dimensional absolute structure.
