\section{Mathematical Preliminaries}
\label{sec:preliminaries}

This section establishes the formal cryptographic and algebraic foundations underpinning Algebirc. We introduce the Ring Learning With Errors (RLWE) problem, define the arithmetic of Genus-2 Hyperelliptic Curves via Mumford representation, and formally structure Richelot Isogenies.

\subsection{Lattices and the RLWE Assumption}
Let $R = \Z[x]/\langle \Phi_m(x) \rangle$ be the ring of integers of the $m$-th cyclotomic field, where $\Phi_m(x)$ is the $m$-th cyclotomic polynomial. For cryptographic efficiency, we restrict our focus to power-of-two cyclotomics where $m = 2N$ and $\Phi_m(x) = x^N + 1$. 
Let $q \ge 2$ be a prime integer, and define the quotient ring $R_q = R / qR = \Z_q[x]/\langle x^N + 1 \rangle$.

\begin{definition}[Decisional RLWE Problem \cite{bv11}]
Let $\chi$ be an error distribution over $R$, typically a discrete Gaussian distribution over the coefficients. Let $\sk \leftarrow \chi$ be a secret uniformly sampled from the error distribution. Let $\mathcal{O}_{\sk}$ be an oracle that outputs samples of the form $(a, b = a \cdot \sk + e \pmod q)$, where $a \leftarrow R_q$ is uniformly random and $e \leftarrow \chi$.
The Decisional RLWE problem states that for any probabilistic polynomial-time (PPT) adversary $\mathcal{A}$, the advantage distinguishing a polynomial number of samples from $\mathcal{O}_{\sk}$ from uniformly random samples in $R_q \times R_q$ is negligible:
\begin{equation}
    \left| \Pr[\mathcal{A}(a_i, a_i \cdot \sk + e_i) = 1] - \Pr[\mathcal{A}(a_i, u_i) = 1] \right| \le \text{negl}(\kappa)
\end{equation}
where $u_i \leftarrow R_q$ and $\kappa$ is the security parameter.
\end{definition}

In Algebirc, the encryption of a plaintext polynomial $m \in R_t$ (for a plaintext modulus $t \ll q$) under a symmetric key $\sk \in R_q$ is defined formally via a scaling factor $\Delta = \lfloor q/t \rfloor$.
\begin{theorem}[Decryption Correctness]
Given ciphertext $c = a \cdot \sk + e + \Delta \cdot m$, the decryption structure $\Dec(c, \sk)$ recovers $m$ if and only if the infinity norm of the error is bounded exactly by $\|e\|_{\infty} < \frac{\Delta}{2}$.
\end{theorem}
\begin{proof}
    The decryption function evaluates the linear phase $c - a \cdot \sk \pmod q$. Substituting the encryption definition yields:
    \begin{align*}
        c - a \cdot \sk &= (a \cdot \sk + e + \Delta \cdot m) - a \cdot \sk \pmod q \\
        &\equiv e + \Delta \cdot m \pmod q
    \end{align*}
    By dividing by $\Delta$ and rounding to the nearest integer field within $t$, we obtain:
    \begin{equation*}
        \lfloor \frac{e + \Delta \cdot m}{\Delta} \rceil = m + \lfloor \frac{e}{\Delta} \rceil \pmod t
    \end{equation*}
    Provided that $e \in [-\frac{\Delta}{2}, \frac{\Delta}{2})$, the division naturally resolves to zero, perfectly retrieving $m$.
\end{proof}

However, when non-linear operations are evaluated iteratively upon the ciphertext space, the magnitude of $e$ inflates geometrically. The phenomenon critically dictates the \textit{Multiplicative Depth Limit} of evaluating S-Boxes homomorphically without bootstrapping, birthing the foundation for our Decrypt-Compute-Reencrypt architecture.

\subsection{Hyperelliptic Curves and Jacobian Arithmetic}
A hyperelliptic curve $C$ of genus $g \ge 1$ over a finite field $\F_p$ is defined implicitly by an affine non-singular formulation. We confine our architecture strictly to $g=2$.

\begin{definition}[Genus-2 Hyperelliptic Curve]
A hyperelliptic curve $C$ over a field $\mathbb{K}$ (where char$(\mathbb{K}) \ne 2$) is given by the equation:
\begin{equation}
    C: y^2 = f(x)
\end{equation}
where $f(x) \in \mathbb{K}[x]$ is a monic polynomial of degree $2g+1 = 5$ with mutually distinct roots, ensuring non-singularity ($\Delta(f) \ne 0$).
\end{definition}

Unlike genus-1 elliptic curves whose points directly constitute an Abelian algebraic group under chord-and-tangent addition, the points on $C$ do not form a group natively. The group structure is instead localized on the \textbf{Jacobian Variety} of the curve, denoted $\J$.

Elements of $\J$ represent equivalence classes of degree-zero divisors under principal divisor equivalence. In modern computation, these elements are uniquely determined by their \textbf{Mumford Representation} $\langle U(x), V(x) \rangle$, defined algorithmically as follows:
\begin{enumerate}
    \item $U(x) = \prod_{i=1}^r (x - x_i)$ is a monic polynomial where bounded degree $r \le g$. The roots $x_i$ project the $x$-coordinates of the points in the support sequence.
    \item $V(x)$ is a bounding mapping polynomial where $\deg(V) < \deg(U)$, constructed such that $V(x_i) = y_i$, interpolating the corresponding $y$-coordinates.
    \item The congruence constraint requires that $f(x) - V(x)^2 \equiv 0 \pmod{U(x)}$.
\end{enumerate}

Addition of two divisors $D_1 = \langle u_1, v_1 \rangle$ and $D_2 = \langle u_2, v_2 \rangle$ in $\J$ is carried out flawlessly using \textbf{Cantor's Algorithm}. 
\begin{algorithm}[H]
\caption{Cantor's Algorithm for Jacobian Addition}\label{alg:cantor}
\begin{algorithmic}[1]
\Require Divisors $D_1 = \langle u_1, v_1 \rangle, D_2 = \langle u_2, v_2 \rangle$ on $\J$
\Ensure Divisor $D_3 = D_1 \oplus D_2 = \langle u_3, v_3 \rangle$
\State $d = \gcd(u_1, u_2, v_1 + v_2)$
\State Find $s_1, s_2, s_3$ such that $d = s_1u_1 + s_2u_2 + s_3(v_1 + v_2)$
\State $u' \gets \frac{u_1 u_2}{d^2}$
\State $v' \gets \frac{s_1 u_1 v_2 + s_2 u_2 v_1 + s_3(v_1 v_2 + f)}{d} \pmod{u'}$
\While{$\deg(u') > g$}
    \State $u' \gets \frac{f - (v')^2}{u'}$ \Comment{Reduction Step}
    \State $v' \gets -v' \pmod{u'}$
\EndWhile
\State \Return $D_3 = \langle u', v' \rangle$
\end{algorithmic}
\end{algorithm}

Cantor's explicitly deterministic mapping ensures that scalar multiplication $[k]D$ can be performed leveraging standard double-and-add frameworks, a property pivotal to executing our \textit{Geometric Branchless Execution} (Section \ref{sec:architecture}).

\subsection{Richelot Isogenies on Genus-2}
An isogeny is formally a rational algebraic morphism $\phi: \J \to \mathcal{J}_{C'}$ between two algebraic groups that preserves the respective identities. While genus-1 isogenies rely heavily on V\'elu's formulas, our architecture obfuscates control flow via \textbf{Richelot Isogenies} for $g=2$.

\begin{definition}[Richelot Map \cite{richelot}]
Let $C: y^2 = G_1(x) G_2(x) G_3(x)$ where $G_1, G_2, G_3 \in \F_p[x]$ are quadratic polynomials. A Richelot isogeny defines a $(2,2)$-mapping to a target curve $C': y^2 = H_1(x) H_2(x) H_3(x)$, where $H_k$ are directly proportional to the scaled determinants of the geometric Jacobians across the $G_k$ roots.
\end{definition}

By evaluating scalar multipliers across distinct mapped Jacobians, the evaluator guarantees mathematically distinct obfuscated outputs, preserving strict bijectivity without explicit branching.
