\begin{abstract}
In this technical report, we present \textsc{Algebirc}, an end-to-end framework for source-code obfuscation grounded in the arithmetic of genus-2 hyperelliptic curves. Traditional software protection relies on heuristic control-flow transformations that are increasingly vulnerable to automated analysis, such as symbolic execution and SMT solvers. \textsc{Algebirc} shifts the security boundary to the algebraic structure of the program's data-flow. Program coefficients are mapped to reduced Mumford divisors on the Jacobian variety $J_\mathcal{C}$ of a genus-2 curve and transported through a walk of $(2,2)$-Richelot isogenies.

We demonstrate that reversing this process without the secret parameters reduces to the Isogeny Path Problem on abelian surfaces, which is believed to be quantum-resistant under specific parameters. The framework includes a highly optimized algebraic core, a precise geometric transport layer, a suite of algebraic leakage analysis tools, an internal polynomial degree tracker, and a standalone metamorphic Ahead-Of-Time (AOT) compiler for tamper-resistant runtime execution.

This document provides a deep architectural dissection, systematic mathematical proofs of correctness, and a comprehensive security review against various mathematical modeling attacks such as Gaussian rank inference, Gröbner basis deflation, and ARX diffusion linearization.
\\[0.5em]
\textbf{Keywords:} Cryptographic Obfuscation, Genus-2 Curves, Richelot Isogeny, Mumford Divisors, Igusa Invariants, Siegel Modular Forms, Haskell.
\end{abstract}

\tableofcontents

\section{Introduction}
\label{sec:intro}

\subsection{The Crisis of Heuristic Obfuscation in Modern Software}
Software security and obfuscation remain critical components in the cybersecurity landscape, primarily for safeguarding intellectual property (IP), preventing reverse engineering, and securing cryptographic models within white-box environments. However, the vast majority of current industry solutions are built atop heuristic "tricks." These approaches include control-flow flattening, arbitrary instruction substitution, dead/junk code insertion, and static string encryption.

Such heuristic methods provide only a superficial layer of protection. Against modern, high-precision automated analysis tools—such as symbolic execution (e.g., Angr), concolic execution, SMT solvers (e.g., Z3), and decompiler analytics (e.g., IDA Pro, Ghidra)—these heuristic transformations collapse almost instantly. These solutions can analyze and normalize the logic flow back to its original state in polynomial time, fundamentally exposing the program without requiring significant mathematical cryptanalysis.

This defines the crisis of heuristic obfuscation: adding increasingly complex "junk" transformations consumes enormous amounts of memory and register manipulation latency, yet the security guarantees can be bypassed merely by detecting and discarding obsolete patterns using standard compiler reduction techniques. This unequivocally demonstrates the urgent need for a new software obfuscation paradigm rooted in \textbf{Provable Security Hardness}.

\subsection{Obfuscation as Algebraic Geometric Transformation}
Faced with these limitations, \textsc{Algebirc} formulates a radical solution by shifting the obfuscation perimeter from syntactic control-flow to the algebraic structural hardness of the data-flow itself. Rather than merely reducing syntactic readability, we exploit the spatial hardness of advanced algebraic geometry.

By mapping actual program data—ranging from Abstract Syntax Tree (AST) coefficients, secret keys, to static strings—into high-dimensional geometric objects, \textsc{Algebirc} directly inherits the cryptographic security properties of Isogeny-based Cryptography.

Internally, data is "lifted" into a polynomial ring using bounded degree representations with a large prime modulus $GF(p)$. Following this, a substitution-permutation network based on a Feistel structure that internally incorporates a Fermat-inverse S-Box is triggered. To achieve full-width dependency diffusion, an Add-Rotate-XOR (ARX) network is configured. Everything is dynamically embedded before being transported to the high-level hyperelliptic curve group system.

\subsection{Primary Technical Contributions}
This work definitively dedicates a systematic architecture and algebraic foundation to the \textsc{Algebirc} framework. We outline several pioneering breakthroughs in software defense and cryptographic architecture:

\begin{enumerate}
    \item \textbf{Lossless Geometric Transport via Kunzweiler Correspondence:} 
    We present a comprehensive, precision-flawless method for transporting AST metadata as scalars, staging them as projective Mumford polynomial elements on Jacobian varieties, and mixing them across an isogeny walk without any loss of information.
    
    \item \textbf{Bypassing $GF(p^2)$ Extension Fields using Sylvester Matrices:}
    Instead of relying on fragile root-finding computations within the $GF(p^2)$ extension field—which severely impacts performance and introduces mathematical vulnerabilities—Algebirc entirely implements a symbolic matrix determinant projector (Sylvester Resultants) purely over $GF(p)$. This maintains extreme engine cohesion.
    
    \item \textbf{Hybrid Security Architecture (Nonlinear \& Geometric):}
    A strategic interleaving of Fermat-inverse based S-Box layers, quadratic Feistel network blocks (guaranteeing a minimum of 3 rounds of proven nonlinearity), ARX full-width diffusion, and Genus-2 Richelot hyperelliptic curve transport, all perfectly sealed together.
    
    \item \textbf{Scalable Karatsuba-based Polynomial Evaluator (Boxed Vectors):}
    Executing highly dense polynomial block multiplications natively incurs $O(n^2)$ computational cost. Algebirc fundamentally resolves this via a recursive $O(n^{1.58})$ Karatsuba Optimizer written natively over contiguous arrays (Unboxed/Boxed Vectors). This strictly prevents invisible truncations when managing giant cryptographic primes (256-bit modulo).

    \item \textbf{Red-Teaming Infrastructure via Gröbner Leakage Analysis:}
    Unlike abstract obfuscation tools that merely provide theoretical assurances, Algebirc integrates a constant-running Adversarial Oracle. This feature autonomously probes for linear row dimension vulnerabilities (Rank Defect), structural invariants, monomial degree leakage traces, and fictitious Gröbner basis complexity estimations per coefficient block.

    \item \textbf{Metamorphic Standalone AOT Compilation Engine:}
    We substitute standard interpretation dependencies by deploying `Algebirc.Compiler.Standalone` to forge self-contained Haskell binaries. The compilation execution dynamically bakes in the primitive ARX evaluator engine, rendering the resulting file completely executable without leaving traces of its native compiler configuration.
\end{enumerate}

Through these advancements, \textsc{Algebirc} sets the absolute parameter for defensive software evolution: rejecting reliance on compiler tricks and fully embracing High-Genus Algebraic Geometry.
